Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-18 paper-webserver.tex
ADD: new para for pipelines

Spfy enables processing of thousands of genome sequences using multiple modules.
By using task queue workers, enabled by the Python-based Redis Queue library \url{https://github.com/nvie/rq}, performance can quickly scale to available infrastructure.
As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} for real-time exception tracking.
Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers.

@@

Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

>>>>

Task queues are processes which schedule code exection across available computing infrastructure.
In Spfy, the Python-based Redis Queue library \url{https://github.com/nvie/rq} is used to schedule analysis tasks and have them run asynchronously in response to user requests.
When a user submits files for analysis or population-wide anlayses, separate tasks are enqueued at different priorities, depending on when users might expect the result to be returned.
For example, population-wide analyses have a higher priority than bulk subtyping analyses, as we expect day-to-day web searches (for example, on Google) to respond instantly whereas a delay in subtyping is typical in similar web services such as the Center for Genomic Epidemiology Pipeline (CGE Pipeline) \cite{thomsen2016bacterial}.
Spfy enables processing of thousands of genome sequences by using task queue workers running in parallel, which also allows performance to scale to available infrastructure.
To ensure reliability of the platform, the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} was integrated and used for real-time exception tracking.

@@

Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers.
Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.
